Subjective Experience of Demands and Resources across O*NET Job Elements

### 2024-03-12 Submission.Rmd
updating introduction

We build on the work of a small, but growing number of researchers who argue that the work elements may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges], with primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics. Prior to presenting the current study in detail, we provide a brief overview of the relevant theories and relevant empirical work on this topic.

*Resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job]. In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is commonly cited as a demand; @demerouti2001job). The perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; @bakker2014job). Of particular importance here is that it is *the perception* of a characteristic or situation that determines which process an employee will experience despite the *a priori* objective assumption of a characteristic as objectively a "demand" or "resource". We explore this further below.

## The Challenge-hindrance Stressor Framework

Although much of our research on job demands based on a priori classifications [@searle2015merits], the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand). @lazarus1984stress's transactional theory of stress and coping suggests that people cognitively appraise stimuli in their environments on a continual basis. If a task or situation is appraised as threatening, challenging, or possibly harmful, the resulting emotional distress initiates a coping response. These primary and secondary appraisals can happen simultaneously. For example, perceiving ample resources to cope with a stressor may influence an employee’s initial appraisal of a stressor (e.g., amount of time [resource] available to prepare for the speech may influence one’s primary appraisal of this task).

@cavanaugh2000empirical delineated between two forms of demands -- *challenges* and *hindrances*. Both are considered stressors [e.g., @cavanaugh2000empirical]. Challenge demands promote mastery, personal growth, and future gains – these stressors should lead to coping strategies that facilitate achievement. Work characteristics consistent with this definition include time pressure and responsibility. Hindrance demands, in contrast, inhibit growth, learning and goal achievement. Hindrance stressors in a work context include role conflict, role ambiguity, and organizational politics. The original work on this topic suggests that challenge stressors are typically associated with positive outcomes and hindrance stressors are associated with negative outcomes [e.g., @cavanaugh2000empirical].

@@

@lepine2022challenge explain the mechanisms by which demands are related to performance and wellbeing outcomes. First, stressors appraised as challenges typically result in a challenge appraisal, and engagement is likely to happen as a result. Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing. Of note is that this energy may be depleted eventually, leading to strain. Stressors appraised as hindrances elicit a different process. Disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing. This happens because resources are depleted via frustrations and other affectively negative reactions [@lepine2022challenge].

@@

Add resources here

We next consider the empirical evidence on this topic. The first question we should ask is whether people distinguish between challenge vs. hindrance demands, or whether all demands are under a larger “demands” category. Evidence suggests the employees do, in fact, differentiate between challenge and hindrance stressors [e.g., @bakker2013weekly; @gerich2017relevance; @webster2011extending]. For example, @bakker2013weekly found that work pressure was perceived as a hindrance demand, and emotional demands as more of a challenge demand. @webster2011extending approached this question with three common workplace demands: workload, role ambiguity, and role conflict. They found while that each could be appraised primarily as a challenge or hindrance demand, they could also simultaneously be perceived as being both a challenge and hindrance demand to different degrees.

>Hypothesis 1: Job characteristics differ in consistancy regarding subjective worker perception as a demand or resource.

@@

@@

## Connecting appraisals to workplace outcomes[^thought]

[^thought]: add a sentence that adds a brief description of working conditions to first paragraph. Whole section needs expansion.

The second set of analyses focuses on associations. Do demands and resources have implications for work outcomes? Appraisals are associated with different forms of coping, and subsequently, outcomes. See Figure \@ref(fig:ourmodel) for proposed associations. The challenge-hindrance stressor framework has been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and wellbeing. A sampling of variables and relationships are described below to provide a sense of scope of the work that has been on this topic. @kim2020thriving found that appraising a demand (in their study, workload, responsibility, and learning demands were measured) as a challenge was associated with motivational resources (i.e., sense of self-worth and work meaningfulness), which were positively related to flourishing. The opposite occurred when a demand was appraised as a hindrance – in those instances, the appraisal had a negative association with motivational resources. @cavanaugh2000empirical, in a study of managers, found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern. @chen2021daily found that daily challenge demands were positively related to cognitive wellbeing and work-family enrichment. Daily hindrance demands were negatively related to these outcomes. In contrast, @abbas2019challenge found that challenge and hindrance stressors were *both* positively related to strain and turnover intentions. We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with it [@crawford2010linking]. Challenge and hindrance appraisals have also been shown to relate to citizenship and counterproductive performance, although indirectly via emotions like anxiety [@rodell2009can]. Lastly, @gerich2017relevance concluded that employee wellbeing was also, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands.

We even have sufficient evidence to explore outcomes associated with challenge and hindrance stressors meta-analytically at this point, and a rich collection of them support differential associations across a variety of organizational outcomes as well. For example, both challenges and hindrances have been shown to positively predict strain [@lepine2005meta; @podsakoff2007differential; @webster2010toward]. Many other outcomes are differentially related to challenges and hindrances, largely in the expected direction. For example, motivation, job satisfaction, commitment, and performance have been shown to positively relate to challenge stressors and negatively relate to hindrance stressors [@lepine2005meta]. Turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance stressors [@podsakoff2007differential]. @kim2020thriving, similarly, found evidence for the differential results via challenge and hindrance appraisals.

>Hyp 3.a: Job resources are associated with greater engagement, less stress, and less burnout.

>Hyp 3.b: More hindrances leads to less engagement, more stress, and greater burnout.

>Hyp 3.exploratory: More challenges leads to greater satisfaction, engagement, and burnout.[^figure]

[^figure]: These need to be reframed to match Figure 1.

>>>>

While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular. We build on the work of a small, but growing number of researchers who argue that the work elements may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges], with primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) explore whether these subjective appraisals are differentially related to positive and negative outcomes. We utilize the O\*Net database (https://www.onetcenter.org/content.html), which is the primary source of occupational information in the US, and as such, provides a rich source of information about occupational requirements (i.e., work activities and context) that may be rated in terms of level of demand or resource. We will refer to these as elements of working conditions throughout this paper (e.g., personal, contextual, or task-related conditions or elements of one's work).

## The Job Demands-Resources Theory and Challenge-hindrance Stressor Framework

Two related theories serve as the foundation for the current study: @demerouti2001job's job demands-resources theory and @cavanaugh2000empirical's later challenge-hindrance stressor framework. First, research on the job demands-resources model @demerouti2001job and later job demands-resources theory @bakker2017job highlights the importance of work characteristics on the experience of motivation and strain as well as other, more distal outcomes. The job demands-resources theory distinguishes between resources and demands. *Resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job]. In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is commonly cited as a demand; @demerouti2001job). The perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; @bakker2014job).

In response to inconsistent findings regarding demands and outcomes, @cavanaugh2000empirical expanded the job demands-resources theory in proposing the challenge-hindrance stressor framework, which draws from @lazarus1984stress's work on stress and coping. The challenge-hindrance stressor framework distinguishes between *two forms of demands* -- *challenges* and *hindrances*. Both are considered stressors [e.g., @cavanaugh2000empirical]. Challenge demands promote mastery, personal growth, and future gains – these stressors should lead to coping strategies that facilitate achievement. Work characteristics consistent with this definition include time pressure and responsibility. Hindrance demands, in contrast, inhibit growth, learning and goal achievement. Hindrance stressors in a work context include role conflict, role ambiguity, and organizational politics.

@@

The original work on this topic suggests that challenge stressors are typically associated with positive outcomes and hindrance stressors are associated with negative outcomes [e.g., @cavanaugh2000empirical]. Meta-analytic explorations of this the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (e.g., performance; [@lepine2005meta] and engagement, [@crawford2010linking]). @lepine2022challenge explain the mechanisms by which demands are related to performance and wellbeing outcomes. First, stressors appraised as challenges typically result in a challenge appraisal, and engagement is likely to happen as a result. Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing. Of note is that this energy may be depleted eventually, leading to strain. Stressors appraised as hindrances elicit a different process. Disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing. This happens because resources are depleted via frustrations and other affectively negative reactions [@lepine2022challenge]. Recent work affirms this appraisal process. @pindek2024dynamic meta-analyzed diary studies of dynamic stressors (i.e., short-term daily experiences of stressors) and concluded that daily challenge stressors had a postive direct association with performance, but a negative indirect association with performance through strain (as described by @lepine2022challenge above). As expected, hindrance stressors had both a direct and indirect (through strain) association with performance [@pindek2024dynamic].

@@

Interestingly, much of our existing knowledge regarding the way these relationships between resources/demands and outcomes (e.g., stress, engagement) function is grounded in the assumption that certain job characteristics can generally be considered to be (positive) resources while others can be considered demands. Even @pindek2024dynamic notes this limitation of a priori classification of characteristics as demands, challenges, or hindrances, as do @horan2020review. In fact, although much of our research on job demands based on a priori classifications [@searle2015merits], the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).

As such, the first question we ask is whether people distinguish between resources, challenges, and  hindrances, and whether a job characteristics might even be considered simultaneously as more than one of these (e.g., both a challenge and a resource). Evidence suggests the employees do, in fact, differentiate between challenge and hindrance stressors [e.g., @bakker2013weekly; @gerich2017relevance; @webster2011extending], at least. For example, @bakker2013weekly found that work pressure was perceived as a hindrance demand, and emotional demands as more of a challenge demand. @webster2011extending approached this question with three common workplace demands: workload, role ambiguity, and role conflict. They found while that each could be appraised primarily as a challenge or hindrance demand, they could also simultaneously be perceived as being both a challenge and hindrance demand to different degrees. We aim to both replicate the above findings and extend them to include resources.

>Hypothesis 1: Job characteristics differ in consistancy regarding subjective worker perception as a challenge or hindrance demand, or resource.

@@

## Connecting Appraisals to Workplace Outcomes

The second set of analyses focuses on predicted associations without outcomes frequently studied across via job demands-resources @bakker2017job and challenge-hindrance stressor framework @cavanaugh2000empirical. Here, we specifically explore O\*Net specified working condition apprasials as resources, challenges, and/or hindrances in association with engagement, strain and burnout. As argued above, appraisals are predicted to be associated with different forms of coping, and subsequently, outcomes. See Figure \@ref(fig:ourmodel) for proposed associations.

@@

Both the job demands-resources model and the challenge-hindrance stressor framework have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and wellbeing. Beginning with resources ADD JDR STUFF ON RESOURCES AND MOTIVATION HERE. A sampling of variables and relationships are described below to provide a sense of scope of the work that has been on this topic. @kim2020thriving found that appraising a demand (in their study, workload, responsibility, and learning demands were measured) as a challenge was associated with motivational resources (i.e., sense of self-worth and work meaningfulness), which were positively related to flourishing. The opposite occurred when a demand was appraised as a hindrance – in those instances, the appraisal had a negative association with motivational resources. @cavanaugh2000empirical, in a study of managers, found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern. @chen2021daily found that daily challenge demands were positively related to cognitive wellbeing and work-family enrichment. Daily hindrance demands were negatively related to these outcomes. In contrast, @abbas2019challenge found that challenge and hindrance stressors were *both* positively related to strain and turnover intentions. We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with it [@crawford2010linking]. Challenge and hindrance appraisals have also been shown to relate to citizenship and counterproductive performance, although indirectly via emotions like anxiety [@rodell2009can]. Lastly, @gerich2017relevance concluded that employee wellbeing was also, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands. In addition to the studies above, several meta-analyses also support differential associations across a variety of organizational outcomes as well. For example, both challenges and hindrances have been shown to positively predict strain [@lepine2005meta; @podsakoff2007differential; @webster2010toward]. Many other outcomes are differentially related to challenges and hindrances, largely in the expected direction. For example, motivation, job satisfaction, commitment, and performance have been shown to positively relate to challenge stressors and negatively relate to hindrance stressors [@lepine2005meta]. Turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance stressors [@podsakoff2007differential]. @kim2020thriving, similarly, found evidence for the differential results via challenge and hindrance appraisals.

>Hyp 3.a: Job resources are positively associated with engagement.

>Hyp 3.b: Challenge stressors are positively associated with engagement, strain, and burnout.

>Hyp 3.c: Hindrance stressors are negatively associated with strain, and burnout.

ADD JDR RESOURCES ACT AS A BUFFER INFO HERE ALONG WITH THESE NEW PREDICTIONS

>Hyp 4.a:Resources moderate the relationship between challenge stressors and the outcomes of strain and burnout such that these relationship become weaker as workers perceive more resources.

>Hyp 4.b:Resources moderate the relationship between hindrance stressors and the outcomes of strain and burnout such that these relationship become weaker as workers perceive more resources.

### 2024-03-12 Submission.tex
tinkering
updating introduction

Research on the job demands-resources model (Demerouti et al., 2001) and later job demands-resources theory (Bakker \& Demerouti, 2017) highlights the importance of work characteristics on the experience of motivation and strain as well as other, more distal outcomes. However, much of our existing knowledge regarding the way these relationships function is grounded in the assumption that certain job characteristics can generally be considered to be (positive) resources while others can be considered demands. We build on the work of a small, but growing number of researchers who argue that the work elements may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020), with primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics. Prior to presenting the current study in detail, we provide a brief overview of the relevant theories and relevant empirical work on this topic.

\hypertarget{the-job-demands-resources-theory}{%
\subsection{The Job demands-Resources Theory}\label{the-job-demands-resources-theory}}

\emph{Resources} include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001). In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is commonly cited as a demand; Demerouti et al. (2001)). The perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; Bakker and Demerouti (2014)). Of particular importance here is that it is \emph{the perception} of a characteristic or situation that determines which process an employee will experience despite the \emph{a priori} objective assumption of a characteristic as objectively a ``demand'' or ``resource''. We explore this further below.

\hypertarget{the-essential-role-of-appraisal}{%
\subsection{The Essential Role of Appraisal}\label{the-essential-role-of-appraisal}}

Although much of our research on job demands based on a priori classifications (Searle \& Auton, 2015), the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand). Lazarus and Folkman (1984)'s transactional theory of stress and coping suggests that people cognitively appraise stimuli in their environments on a continual basis. If a task or situation is appraised as threatening, challenging, or possibly harmful, the resulting emotional distress initiates a coping response. These primary and secondary appraisals can happen simultaneously. For example, perceiving ample resources to cope with a stressor may influence an employee's initial appraisal of a stressor (e.g., amount of time {[}resource{]} available to prepare for the speech may influence one's primary appraisal of this task).

\hypertarget{the-challenge-hindrance-stressor-framework}{%
\subsection{The Challenge-hindrance Stressor Framework}\label{the-challenge-hindrance-stressor-framework}}

Demand --\textgreater{} appraisal (as challenge or hindrance)

Demand=Stressor

Decision (can overcome or not )

Cavanaugh et al. (2000) delineated between two forms of demands -- \emph{challenges} and \emph{hindrances}. Both are considered stressors (e.g., Cavanaugh et al., 2000). Challenge demands promote mastery, personal growth, and future gains -- these stressors should lead to coping strategies that facilitate achievement. Work characteristics consistent with this definition include time pressure and responsibility. Hindrance demands, in contrast, inhibit growth, learning and goal achievement. Hindrance stressors in a work context include role conflict, role ambiguity, and organizational politics. The original work on this topic suggests that challenge stressors are typically associated with positive outcomes and hindrance stressors are associated with negative outcomes (e.g., Cavanaugh et al., 2000).

M. A. LePine (2022) explain the mechanisms by which demands are related to performance and wellbeing outcomes. First, stressors appraised as challenges typically result in a challenge appraisal, and engagement is likely to happen as a result. Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing. Of note is that this energy may be depleted eventually, leading to strain. Stressors appraised as hindrances elicit a different process. Disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing. This happens because resources are depleted via frustrations and other affectively negative reactions (M. A. LePine, 2022).

\hypertarget{argue-for-h1-and-h2-are-perceptions-universal}{%
\subsection{ARGUE FOR H1 and H2 (Are perceptions universal?)}\label{argue-for-h1-and-h2-are-perceptions-universal}}

Add resources here

We next consider the empirical evidence on this topic. The first question we should ask is whether people distinguish between challenge vs.~hindrance demands, or whether all demands are under a larger ``demands'' category. Evidence suggests the employees do, in fact, differentiate between challenge and hindrance stressors (e.g., Bakker \& Sanz-Vergel, 2013; Gerich, 2017; Webster et al., 2011). For example, Bakker and Sanz-Vergel (2013) found that work pressure was perceived as a hindrance demand, and emotional demands as more of a challenge demand. Webster et al. (2011) approached this question with three common workplace demands: workload, role ambiguity, and role conflict. They found while that each could be appraised primarily as a challenge or hindrance demand, they could also simultaneously be perceived as being both a challenge and hindrance demand to different degrees.

\begin{quote}
Hypothesis 1: Job characteristics differ in consistancy regarding subjective worker perception as a demand or resource.
\end{quote}

@@

@@

\hypertarget{connecting-appraisals-to-workplace-outcomesthought}{%
\subsection[Connecting appraisals to workplace outcomes]{\texorpdfstring{Connecting appraisals to workplace outcomes\footnote{add a sentence that adds a brief description of working conditions to first paragraph. Whole section needs expansion.}}{Connecting appraisals to workplace outcomes}}\label{connecting-appraisals-to-workplace-outcomesthought}}

The second set of analyses focuses on associations. Do demands and resources have implications for work outcomes? Appraisals are associated with different forms of coping, and subsequently, outcomes. See Figure \ref{fig:ourmodel} for proposed associations. The challenge-hindrance stressor framework has been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and wellbeing. A sampling of variables and relationships are described below to provide a sense of scope of the work that has been on this topic. Kim and Beehr (2020) found that appraising a demand (in their study, workload, responsibility, and learning demands were measured) as a challenge was associated with motivational resources (i.e., sense of self-worth and work meaningfulness), which were positively related to flourishing. The opposite occurred when a demand was appraised as a hindrance -- in those instances, the appraisal had a negative association with motivational resources. Cavanaugh et al. (2000), in a study of managers, found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern. Chen et al. (2021) found that daily challenge demands were positively related to cognitive wellbeing and work-family enrichment. Daily hindrance demands were negatively related to these outcomes. In contrast, Abbas and Raja (2019) found that challenge and hindrance stressors were \emph{both} positively related to strain and turnover intentions. We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with it (Crawford et al., 2010). Challenge and hindrance appraisals have also been shown to relate to citizenship and counterproductive performance, although indirectly via emotions like anxiety (Rodell \& Judge, 2009). Lastly, Gerich (2017) concluded that employee wellbeing was also, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands.

We even have sufficient evidence to explore outcomes associated with challenge and hindrance stressors meta-analytically at this point, and a rich collection of them support differential associations across a variety of organizational outcomes as well. For example, both challenges and hindrances have been shown to positively predict strain (J. A. LePine et al., 2005; Podsakoff et al., 2007; Webster et al., 2010). Many other outcomes are differentially related to challenges and hindrances, largely in the expected direction. For example, motivation, job satisfaction, commitment, and performance have been shown to positively relate to challenge stressors and negatively relate to hindrance stressors (J. A. LePine et al., 2005). Turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance stressors (Podsakoff et al., 2007). Kim and Beehr (2020), similarly, found evidence for the differential results via challenge and hindrance appraisals.

\hypertarget{current-study-and-hypotheses}{%
\subsection{Current Study and Hypotheses}\label{current-study-and-hypotheses}}

\begin{quote}
Hyp 3.a: Job resources are associated with greater engagement, less stress, and less burnout.
\end{quote}

\begin{quote}
Hyp 3.b: More hindrances leads to less engagement, more stress, and greater burnout.
\end{quote}

\begin{quote}
Hyp 3.exploratory: More challenges leads to greater satisfaction, engagement, and burnout.\footnote{These need to be reframed to match Figure 1.}
\end{quote}

@@

>>>>

While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular. We build on the work of a small, but growing number of researchers who argue that the work elements may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020), with primary aims of exploring 1) whether there is variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands, and 2) explore whether these subjective appraisals are differentially related to positive and negative outcomes. We utilize the O*Net database (\url{https://www.onetcenter.org/content.html}), which is the primary source of occupational information in the US, and as such, provides a rich source of information about occupational requirements (i.e., work activities and context) that may be rated in terms of level of demand or resource. We will refer to these as elements of working conditions throughout this paper (e.g., personal, contextual, or task-related conditions or elements of one's work).

\hypertarget{the-job-demands-resources-theory-and-challenge-hindrance-stressor-framework}{%
\subsection{The Job Demands-Resources Theory and Challenge-hindrance Stressor Framework}\label{the-job-demands-resources-theory-and-challenge-hindrance-stressor-framework}}

Two related theories serve as the foundation for the current study: Demerouti et al. (2001)'s job demands-resources theory and Cavanaugh et al. (2000)'s later challenge-hindrance stressor framework. First, research on the job demands-resources model Demerouti et al. (2001) and later job demands-resources theory Bakker and Demerouti (2017) highlights the importance of work characteristics on the experience of motivation and strain as well as other, more distal outcomes. The job demands-resources theory distinguishes between resources and demands. \emph{Resources} include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001). In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is commonly cited as a demand; Demerouti et al. (2001)). The perception of an element of one's job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources; Bakker and Demerouti (2014)).

In response to inconsistent findings regarding demands and outcomes, Cavanaugh et al. (2000) expanded the job demands-resources theory in proposing the challenge-hindrance stressor framework, which draws from Lazarus and Folkman (1984)'s work on stress and coping. The challenge-hindrance stressor framework distinguishes between \emph{two forms of demands} -- \emph{challenges} and \emph{hindrances}. Both are considered stressors (e.g., Cavanaugh et al., 2000). Challenge demands promote mastery, personal growth, and future gains -- these stressors should lead to coping strategies that facilitate achievement. Work characteristics consistent with this definition include time pressure and responsibility. Hindrance demands, in contrast, inhibit growth, learning and goal achievement. Hindrance stressors in a work context include role conflict, role ambiguity, and organizational politics.

The original work on this topic suggests that challenge stressors are typically associated with positive outcomes and hindrance stressors are associated with negative outcomes (e.g., Cavanaugh et al., 2000). Meta-analytic explorations of this the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (e.g., performance; (J. A. LePine et al., 2005) and engagement, (Crawford et al., 2010)). M. A. LePine (2022) explain the mechanisms by which demands are related to performance and wellbeing outcomes. First, stressors appraised as challenges typically result in a challenge appraisal, and engagement is likely to happen as a result. Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing. Of note is that this energy may be depleted eventually, leading to strain. Stressors appraised as hindrances elicit a different process. Disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing. This happens because resources are depleted via frustrations and other affectively negative reactions (M. A. LePine, 2022). Recent work affirms this appraisal process. Pindek et al. (2024) meta-analyzed diary studies of dynamic stressors (i.e., short-term daily experiences of stressors) and concluded that daily challenge stressors had a postive direct association with performance, but a negative indirect association with performance through strain (as described by M. A. LePine (2022) above). As expected, hindrance stressors had both a direct and indirect (through strain) association with performance (Pindek et al., 2024).

\hypertarget{are-perceptions-of-job-resources-challenge-demands-and-hindrance-demands-universal}{%
\subsection{Are Perceptions of Job Resources, Challenge Demands, and Hindrance Demands Universal?}\label{are-perceptions-of-job-resources-challenge-demands-and-hindrance-demands-universal}}

Interestingly, much of our existing knowledge regarding the way these relationships between resources/demands and outcomes (e.g., stress, engagement) function is grounded in the assumption that certain job characteristics can generally be considered to be (positive) resources while others can be considered demands. Even Pindek et al. (2024) notes this limitation of a priori classification of characteristics as demands, challenges, or hindrances, as do Horan et al. (2020). In fact, although much of our research on job demands based on a priori classifications (Searle \& Auton, 2015), the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).

As such, the first question we ask is whether people distinguish between resources, challenges, and hindrances, and whether a job characteristics might even be considered simultaneously as more than one of these (e.g., both a challenge and a resource). Evidence suggests the employees do, in fact, differentiate between challenge and hindrance stressors (e.g., Bakker \& Sanz-Vergel, 2013; Gerich, 2017; Webster et al., 2011), at least. For example, Bakker and Sanz-Vergel (2013) found that work pressure was perceived as a hindrance demand, and emotional demands as more of a challenge demand. Webster et al. (2011) approached this question with three common workplace demands: workload, role ambiguity, and role conflict. They found while that each could be appraised primarily as a challenge or hindrance demand, they could also simultaneously be perceived as being both a challenge and hindrance demand to different degrees. We aim to both replicate the above findings and extend them to include resources.

\begin{quote}
Hypothesis 1: Job characteristics differ in consistancy regarding subjective worker perception as a challenge or hindrance demand, or resource.
\end{quote}

@@

\hypertarget{connecting-appraisals-to-workplace-outcomes}{%
\subsection{Connecting Appraisals to Workplace Outcomes}\label{connecting-appraisals-to-workplace-outcomes}}

The second set of analyses focuses on predicted associations without outcomes frequently studied across via job demands-resources Bakker and Demerouti (2017) and challenge-hindrance stressor framework Cavanaugh et al. (2000). Here, we specifically explore O*Net specified working condition apprasials as resources, challenges, and/or hindrances in association with engagement, strain and burnout. As argued above, appraisals are predicted to be associated with different forms of coping, and subsequently, outcomes. See Figure \ref{fig:ourmodel} for proposed associations.

@@

Both the job demands-resources model and the challenge-hindrance stressor framework have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, performance, and wellbeing. Beginning with resources ADD JDR STUFF ON RESOURCES AND MOTIVATION HERE. A sampling of variables and relationships are described below to provide a sense of scope of the work that has been on this topic. Kim and Beehr (2020) found that appraising a demand (in their study, workload, responsibility, and learning demands were measured) as a challenge was associated with motivational resources (i.e., sense of self-worth and work meaningfulness), which were positively related to flourishing. The opposite occurred when a demand was appraised as a hindrance -- in those instances, the appraisal had a negative association with motivational resources. Cavanaugh et al. (2000), in a study of managers, found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hindrance demands demonstrated the opposite pattern. Chen et al. (2021) found that daily challenge demands were positively related to cognitive wellbeing and work-family enrichment. Daily hindrance demands were negatively related to these outcomes. In contrast, Abbas and Raja (2019) found that challenge and hindrance stressors were \emph{both} positively related to strain and turnover intentions. We also have some evidence that challenge-hindrance appraisals are related to engagement in the expected direction whereby hindrance appraisals are negatively associated with engagement and challenge appraisals are positively associated with it (Crawford et al., 2010). Challenge and hindrance appraisals have also been shown to relate to citizenship and counterproductive performance, although indirectly via emotions like anxiety (Rodell \& Judge, 2009). Lastly, Gerich (2017) concluded that employee wellbeing was also, in part, explained by appraised challenge or hindrance demands such that working conditions of time pressure, qualitative demands, responsibility, and interruptions, were partially mediated by challenge and hindrance demands. In addition to the studies above, several meta-analyses also support differential associations across a variety of organizational outcomes as well. For example, both challenges and hindrances have been shown to positively predict strain (J. A. LePine et al., 2005; Podsakoff et al., 2007; Webster et al., 2010). Many other outcomes are differentially related to challenges and hindrances, largely in the expected direction. For example, motivation, job satisfaction, commitment, and performance have been shown to positively relate to challenge stressors and negatively relate to hindrance stressors (J. A. LePine et al., 2005). Turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance stressors (Podsakoff et al., 2007). Kim and Beehr (2020), similarly, found evidence for the differential results via challenge and hindrance appraisals.

\begin{quote}
Hyp 3.a: Job resources are positively associated with engagement.
\end{quote}

\begin{quote}
Hyp 3.b: Challenge stressors are positively associated with engagement, strain, and burnout.
\end{quote}

\begin{quote}
Hyp 3.c: Hindrance stressors are negatively associated with strain, and burnout.
\end{quote}

ADD JDR RESOURCES ACT AS A BUFFER INFO HERE ALONG WITH THESE NEW PREDICTIONS

\begin{quote}
Hyp 4.a:Resources moderate the relationship between challenge stressors and the outcomes of strain and burnout such that these relationship become weaker as workers perceive more resources.
\end{quote}

\begin{quote}
Hyp 4.b:Resources moderate the relationship between hindrance stressors and the outcomes of strain and burnout such that these relationship become weaker as workers perceive more resources.
\end{quote}

@@

\leavevmode\vadjust pre{\hypertarget{ref-pindek2024dynamic}{}}%
Pindek, S., Meyer, K., Valvo, A., \& Arvan, M. (2024). A dynamic view of the challenge-hindrance stressor framework: A meta-analysis of daily diary studies. \emph{Journal of Business and Psychology}, 1--19.
